---
title: "Homework 4"
author: "Miguel Salazar"
date: "May 1, 2016"
output: word_document
---

###Problem I

A)
```{r,echo=FALSE}
Prob1 = function(n){
  Does_HW = replicate(n,sample(c("Yes","No"),1, replace = TRUE, prob = c(0.95,0.05)))
  return(sum(Does_HW == "No"))
}
Prob1(40)
```

B) 
```{r,echo=FALSE}

hist(rbinom(1000000, 40, 0.05))
```

C) 
The distribution is not symmetric because it does not have a bell shaped curve. 

D) 
The most frequent number of successes is 2 out of the 40 students, which means they did not do their hw.

```{r,echo=FALSE}
table(rbinom(1000000,40,0.05))
```

### Problem II

A) The average of the number of successes in 40 trials and the standard deviation
```{r,echo=FALSE}
m = mean(rbinom(1000000,40,0.05))
std = sd(rbinom(1000000,40,0.05))
result = cbind(m,std)
colnames(result) = c("mean","std dev")
result
```

B) The probability that all students turned in their homework 
```{r,echo=FALSE}
P = function(x){
bin = rbinom(x, 40, 0.05)
ans = sum(bin == 0)/x
return(ans)
}
P(1000000)
```

C) The probability that at least two students did not turn in their homework
```{r,echo=FALSE}
P = function(x){
bin = rbinom(x, 40, 0.05)
ans = sum(bin >= 2)/x
return(ans)
}
P(1000000)
```

D)
```{r,echo=FALSE}
P = function(x){
bin = rbinom(x, 40, 0.05)
ans = median(bin > 0)
return(ans)
}
P(1000000)
```

###Problem III

```{r,echo=FALSE}
lynx = as.numeric(lynx)
```

A)
```{r, echo=FALSE}
hist(lynx, main = "Population")
a = mean(lynx)
b = sd(lynx)
c = var(lynx)
ans = cbind(a,b,c)
colnames(ans) = c("mean", "std dev", "variance")
ans
```
The population is not normally distributed because it does not have a bell shaped curve.

B)
```{r, echo=FALSE}
mean(sample(lynx,10,replace = TRUE))

```

C)
```{r, echo=FALSE}
x = replicate(1000000,mean(sample(lynx,10)))
mean(x)
sd(x)
```

D)
They were very similar with a differece of 0.165. Therefore both of the means are closely related. The standard deviation for both differed greatly since I got 1585.844 for the std dev for part c and 478.7804 for part a.

### Problem IV

A)
```{r, echo=FALSE}
x = replicate(1000000,mean(sample(lynx,10)))
hist(x)
```
This histogram is less skewed and has a bell shaped curve(normally distributed).

B)
```{r,echo=FALSE}
y = sample(lynx,50)
mean(y)
sd(y)
```

C)
```{r,echo=FALSE}
y = replicate(1000000,mean(sample(lynx,50)))
mean(y)
sd(y)
```
The mean increased slightly and the standard deviation decrease a great amount from 1426 to 168.

D)
```{r,echo=FALSE}
y = replicate(1000000,mean(sample(lynx,50)))
hist(y)
```
The shape is a bell curve.



