---
title: "Homework6"
author: "Miguel Salazar"
date: "May 23, 2016"
output: word_document
---

###Problem I

A)
```{r, echo=FALSE}
normal.pop = rnorm(1000000, mean = 5,sd = 10)
mu = 5

CI = function(x,n,i,mu){
  s = sample(x,n,replace = FALSE)
  std_dev = sd(s)
  u = mean(s)
  t = qt((1-i)/2,n-1)
  
  upper.bound = u + (abs(t)*(std_dev/sqrt(n)))
  lower.bound = u - (abs(t)*(std_dev/sqrt(n)))
  ans = 0
  if(mu >= lower.bound & mu <= upper.bound){
    ans = ans + 1
  }
  return(ans)
}

CI(normal.pop,15,0.95,mu)
```

B)
```{r, echo=FALSE}
normal.pop = rnorm(1000000, mean = 5,sd = 10)
mu = 5
CI = function(x,n,i,mu){
  s = sample(x,n,replace = FALSE)
  std_dev = sd(s)
  u = mean(s)
  t = qt((1-i)/2,n-1)
  
  upper.bound = u + (abs(t)*(std_dev/sqrt(n)))
  lower.bound = u - (abs(t)*(std_dev/sqrt(n)))
  ans = 0
  if(mu >= lower.bound & mu <= upper.bound){
    ans = ans + 1
  }
  return(ans)
}

r = replicate(10000,CI(normal.pop,15,0.95,mu))
table(r)
```

C) Coverage Probability
```{r, echo=FALSE}
t = table(r)
p = t[2]/10000 
p
```

D)
Yes, this confidence interval has a 95 coverage probability, since the coverage probability (0.9515) is greater than .95.


###Problem II

A)
```{r, echo=FALSE}
mu = 5
exp.pop = rexp(1000000,1/mu)

CI = function(x,n,i,mu){
  s = sample(x,n,replace = FALSE)
  std_dev = sd(s)
  u = mean(s)
  t = qt((1-i)/2,n-1)
  
  upper.bound = u + (abs(t)*(std_dev/sqrt(n)))
  lower.bound = u - (abs(t)*(std_dev/sqrt(n)))
  ans = 0
  if(mu >= lower.bound & mu <= upper.bound){
    ans = ans + 1
  }
  return(ans)
}

CI(exp.pop,15,0.95,mu)

```

B)
```{r, echo=FALSE}
mu = 5
exp.pop = rexp(1000000,1/mu)

CI = function(x,n,i,mu){
  s = sample(x,n,replace = FALSE)
  std_dev = sd(s)
  u = mean(s)
  t = qt((1-i)/2,n-1)
  
  upper.bound = u + (abs(t)*(std_dev/sqrt(n)))
  lower.bound = u - (abs(t)*(std_dev/sqrt(n)))
  ans = 0
  if(mu >= lower.bound & mu <= upper.bound){
    ans = ans + 1
  }
  return(ans)
}

r2 = replicate(10000,CI(exp.pop,15,0.95,mu))
table(r2)


```

C)
```{r, echo=FALSE}
t2 = table(r2)
p2 = t2[2]/10000 
p2

```

D)
No this confidence interval did not have a 95 coverage probability, since the probability lies under 95 percent (.9123 < .95).


###Problem III

A)

```{r,echo=FALSE}
mu = 5
exp.pop = rexp(1000000,1/mu)
CI = function(x,n,i,mu){
  s = sample(x,n,replace = FALSE)
  std_dev = sd(s)
  u = mean(s)
  t = qt((1-i)/2,n-1)
  
  upper.bound = u + (abs(t)*(std_dev/sqrt(n)))
  lower.bound = u - (abs(t)*(std_dev/sqrt(n)))
  ans = 0
  if(mu >= lower.bound & mu <= upper.bound){
    ans = ans + 1
  }
  return(ans)
}

CI(exp.pop,60,0.95,mu)

```

B)
```{r,echo=FALSE}
mu = 5
exp.pop = rexp(1000000,1/mu)

CI = function(x,n,i,mu){
  s = sample(x,n,replace = FALSE)
  std_dev = sd(s)
  u = mean(s)
  t = qt((1-i)/2,n-1)
  
  upper.bound = u + (abs(t)*(std_dev/sqrt(n)))
  lower.bound = u - (abs(t)*(std_dev/sqrt(n)))
  ans = 0
  if(mu >= lower.bound & mu <= upper.bound){
    ans = ans + 1
  }
  return(ans)
}

r3 = replicate(10000,CI(exp.pop,60,0.95,mu))
table(r3)

```

C)
```{r,echo=FALSE}
t3 = table(r3)
p3 = t3[2]/10000 
p3

```

D)
No this confidence interval did not have a 95 coverage probability, since the probability lies under 95 percent (.9372 < .95).

********
###Code Appendix

```{r,eval=FALSE}
A)
normal.pop = rnorm(1000000, mean = 5,sd = 10)
mu = 5

CI = function(x,n,i,mu){
  s = sample(x,n,replace = FALSE)
  std_dev = sd(s)
  u = mean(s)
  t = qt((1-i)/2,n-1)
  
  upper.bound = u + (abs(t)*(std_dev/sqrt(n)))
  lower.bound = u - (abs(t)*(std_dev/sqrt(n)))
  ans = 0
  if(mu >= lower.bound & mu <= upper.bound){
    ans = ans + 1
  }
  return(ans)
}

CI(normal.pop,15,0.95,mu)


#B)
normal.pop = rnorm(1000000, mean = 5,sd = 10)
mu = 5
CI = function(x,n,i,mu){
  s = sample(x,n,replace = FALSE)
  std_dev = sd(s)
  u = mean(s)
  t = qt((1-i)/2,n-1)
  
  upper.bound = u + (abs(t)*(std_dev/sqrt(n)))
  lower.bound = u - (abs(t)*(std_dev/sqrt(n)))
  ans = 0
  if(mu >= lower.bound & mu <= upper.bound){
    ans = ans + 1
  }
  return(ans)
}

r = replicate(10000,CI(normal.pop,15,0.95,mu))
table(r)


#C) Coverage Probability

t = table(r)
p = t[2]/10000 
p



###Problem II

#A)

mu = 5
exp.pop = rexp(1000000,1/mu)
CI = function(x,n,i,mu){
  s = sample(x,n,replace = FALSE)
  std_dev = sd(s)
  u = mean(s)
  t = qt((1-i)/2,n-1)
  
  upper.bound = u + (abs(t)*(std_dev/sqrt(n)))
  lower.bound = u - (abs(t)*(std_dev/sqrt(n)))
  ans = 0
  if(mu >= lower.bound & mu <= upper.bound){
    ans = ans + 1
  }
  return(ans)
}

CI(exp.pop,15,0.95,mu)



#B)

mu = 5
exp.pop = rexp(1000000,1/mu)

CI = function(x,n,i,mu){
  s = sample(x,n,replace = FALSE)
  std_dev = sd(s)
  u = mean(s)
  t = qt((1-i)/2,n-1)
  
  upper.bound = u + (abs(t)*(std_dev/sqrt(n)))
  lower.bound = u - (abs(t)*(std_dev/sqrt(n)))
  ans = 0
  if(mu >= lower.bound & mu <= upper.bound){
    ans = ans + 1
  }
  return(ans)
}

r2 = replicate(10000,CI(exp.pop,15,0.95,mu))
table(r2)




#C)

t2 = table(r2)
p2 = t2[2]/10000 
p2




###Problem III

#A)


mu = 5
exp.pop = rexp(1000000,1/mu)
CI = function(x,n,i,mu){
  s = sample(x,n,replace = FALSE)
  std_dev = sd(s)
  u = mean(s)
  t = qt((1-i)/2,n-1)
  
  upper.bound = u + (abs(t)*(std_dev/sqrt(n)))
  lower.bound = u - (abs(t)*(std_dev/sqrt(n)))
  ans = 0
  if(mu >= lower.bound & mu <= upper.bound){
    ans = ans + 1
  }
  return(ans)
}

CI(exp.pop,60,0.95,mu)



#B)

mu = 5
exp.pop = rexp(1000000,1/mu)

CI = function(x,n,i,mu){
  s = sample(x,n,replace = FALSE)
  std_dev = sd(s)
  u = mean(s)
  t = qt((1-i)/2,n-1)
  
  upper.bound = u + (abs(t)*(std_dev/sqrt(n)))
  lower.bound = u - (abs(t)*(std_dev/sqrt(n)))
  ans = 0
  if(mu >= lower.bound & mu <= upper.bound){
    ans = ans + 1
  }
  return(ans)
}

r3 = replicate(10000,CI(exp.pop,60,0.95,mu))
table(r3)



#C)

t3 = table(r3)
p3 = t3[2]/10000 
p3


