---
title: "Homework 5"
author: "Miguel Salazar"
date: "May 10, 2016"
output: word_document
---

### Problem I

A)
```{r,echo=FALSE}

rainy_day = sapply(1:1,function(i){
  rain = 0
  run_time = 0
  while(rain[1] != 1){
    run_time = run_time + 1
    rain = sample(c(0,1),1, prob = c(0.90,0.10))
    }
  ans = run_time
  return(ans)
})
mean(rainy_day)

```

B)

```{r, echo=FALSE}

#a = replicate(20000,rgeom(1,0.10))
#hist(a, main = "20000 trials of X ~ Geometric(0.10)")

rainy_day = sapply(1:20000,function(i){
  rain = 0
  run_time = 0
  while(rain[1] != 1){
    run_time = run_time + 1
    rain = sample(c(0,1),1, prob = c(0.90,0.10))
    }
  ans = run_time
  return(ans)
})
hist(rainy_day,main = "20000 trials of X ~ Geometric(0.10)", xlab = "Number of Days")

```

C)
The greatest frequency for is between 0-5. Then decreases as we get closer to 80. Thus this curves shows a great number of decrease because it is less like to take 80 days for the first day of rain. 

D)
```{r, echo=FALSE}
rainy_day = sapply(1:20000,function(i){
  rain = 0
  run_time = 0
  while(rain[1] != 1){
    run_time = run_time + 1
    rain = sample(c(0,1),1, prob = c(0.90,0.10))
    }
  ans = run_time
  return(ans)
})

mean(rainy_day)
sd(rainy_day)
```

E) The probability that it took 15 days until the first rainy day
```{r, echo=FALSE}
P = function(n){
rainy_day = sapply(1:n,function(i){
  rain = 0
  run_time = 0
  while(rain[1] != 1){
    run_time = run_time + 1
    rain = sample(c(0,1),1, prob = c(0.90,0.10))
    }
  ans = run_time
  return(ans)
})

return(mean(rainy_day == 15))
}

P(20000)
```

F) P( x = 5 | x > 10)
```{r, echo=FALSE}
P = function(n){
rainy_day = sapply(1:n,function(i){
  rain = 0
  run_time = 0
  while(rain[1] != 1){
    run_time = run_time + 1
    rain = sample(c(0,1),1, prob = c(0.90,0.10))
    }
  ans = run_time
  return(ans)
})

A = mean(rainy_day > 10)
B = mean(rainy_day > 15)
A_and_B = A*B
ans = A_and_B / B
return(ans)
}

P(20000)
```

###Problem II

A)
```{r, echo=FALSE}
number = 0
s = 0
counter = 0
while(counter != 5){
  number = number + 1
  s = sample(c(0,1),1, prob = c(0.60,0.40))
  counter = counter + (s == 1)
}

number

```

B) 20000 trials
```{r, echo=FALSE}

Glasses = sapply(1:20000,function(i){
number = 0
s = 0
counter = 0
while(counter != 5){
  number = number + 1
  s = sample(c(0,1),1, prob = c(0.60,0.40))
  counter = counter + (s == 1)
}

return(number)
})

hist(Glasses,main = "20000 trials of X ~ Geometric(0.40)", xlab = "Number of Days")
```

C) Median
```{r,echo=FALSE}
Glasses = sapply(1:20000,function(i){
number = 0
s = 0
counter = 0
while(counter != 5){
  number = number + 1
  s = sample(c(0,1),1, prob = c(0.60,0.40))
  counter = counter + (s == 1)
}

return(number)
})

median(Glasses)

```

D) Median & Std Dev
```{r,echo=FALSE}
Glasses = sapply(1:20000,function(i){
number = 0
s = 0
counter = 0
while(counter != 5){
  number = number + 1
  s = sample(c(0,1),1, prob = c(0.60,0.40))
  counter = counter + (s == 1)
}

return(number)
})

mean(Glasses)
sd(Glasses)

```

E)
```{r,echo=FALSE}

P = function(n){
Glasses = sapply(1:n,function(i){
number = 0
s = 0
counter = 0
while(counter != 5){
  number = number + 1
  s = sample(c(0,1),1, prob = c(0.60,0.40))
  counter = counter + (s == 1)
}

return(number)
})
return(mean(Glasses > 10))

}

P(20000)

```


F)
```{r,echo=FALSE}

P = function(n){
Glasses = sapply(1:n,function(i){
number = 0
s = 0
counter = 0
while(counter != 5){
  number = number + 1
  s = sample(c(0,1),1, prob = c(0.60,0.40))
  counter = counter + (s == 1)
}

return(number)
})
A = mean(Glasses > 10)
B = mean(Glasses > 15)
A_and_B = A*B
ans = A_and_B / B
return(ans)

}

P(20000)

```

### Problem III

A) Mean and Standard devation of X & Y
```{r,echo=FALSE}

X = rnorm(10000, mean = 2, sd = 1)
Y = rnorm(10000, mean = -2, sd = 5)

m = mean(X)
std_dev = sd(X)
ans1 = cbind(m,std_dev)
ans1

m2 = mean(Y)
std_dev2 = sd(Y)
ans2 = cbind(m2,std_dev2)
ans2
```


B) Mean & Standard Deviation of W = X + Y
```{r,echo=FALSE}
X = rnorm(10000, mean = 2, sd = 1)
Y = rnorm(10000, mean = -2, sd = 5)

W = X + Y
mean(W)
sd(W)

```


C) P(W > 3)
```{r,echo=FALSE}
X = rnorm(10000, mean = 2, sd = 1)
Y = rnorm(10000, mean = -2, sd = 5)

W = X + Y
p = sum(W > 3)/length(W)
p

```

D) Error
```{r,echo=FALSE}
m = 10000*(2) + 10000*(-2)
std_dev = sqrt(1 + 25)

error_mean = m - mean(W)
error_sd = std_dev - sd(W)

error_mean
error_sd

z = (3-0)/std_dev
error_prob = p - (1-pnorm(z)) 

error_prob
```

